\documentclass{article}
\usepackage[a4paper, total={6in, 9in}]{geometry}
\title{\textbf{$\Delta$0:3 Spec Sheet}}
\author{Donatas Mockus}
\date{\today}

\begin{document}
\maketitle

\section{Firmware Features}
\begin{itemize}
	\item Bluetooth remote control.
	
	Set the \textit{Activation} switch to \textit{Armed} position for the unit to be activated remotely via bluetooth.
	\item Programmable output wattage.
	\item Programmable output voltage.
	\item Timed activation.
	\item Automatic fuse resistance check.
	\item Calibrator for output cable resistance.
	
	The user would have to manually enter the resistance of the output wires leading to and back from the fuse in order to have accurate power regulation.
	\item Password protected access, activation, and or deactivation.
	
	Passwords are stored on the Atmega EEPROM.
	\item Timed pulse setting for outputting current for a selected time.
	\item Timer post-countdown for measuring when the fuse blows out.
	\item Fuse current, voltage potential, resistance, and output power display.
	\item Stealth mode, shuts screen and any LEDs down during operation.
	\item Battery voltage display.



\end{itemize}



\section{Hardware Features}
\begin{itemize}
	\item \textit{Atmega2560} microprocessor.
	\item OLED or LCD display.
	
	Size debatable.
	\item Bluetooth module allowing for remote controll of the unit.
	\item External power connection.
	\item Internal \textit{18650} battery.
	
	Independant internal power allowing for a fully integrated operation of the unit. A switch allows you to select either internal or external 	battery mode.
	\item Boost converter to step up input voltage.
	\item PWM late stage MOSFET voltage regulator to step down output voltage and controll the output power.
	\item \textit{ACS712} or \textit{ACS758} hall effect current sensor for measuring output current.
	\item Internal battery charging protection.
	\item Buck converters for powering internal devices.
	\item Rotary encoder for navigating menus.
	\item External USB connector allowing for easy interface for reflashing firmware without disassembling the unit.
	\item Three pole DPDT
	\item Buzzer.
	\item Reverse polarity protection.
	\item GX16 connectors.
	\item Extruded aluminium case.
\end{itemize}


\section{Considered Features}

\begin{itemize}
	\item SMT components
	Pros:
	\begin{itemize}
		\item Smaller form factor.
	\end{itemize}
	Cons:
	\begin{itemize}
		\item Requiring ordering of new parts and additional costs.
		\item Questionable ability to solder them.
	\end{itemize}
\end{itemize}



\section{Bill of Materials}
%To purchase:
Already acquired:

\begin{itemize}
	\item Extruded aluminium enclosure, 120x97x40.
	\item PCB.
	\item 1.8" LCD.
	\item 12 button keypad.
	\item DPDT switch, optional protextive cover.
	\item Buck converters.
	\item Boost converter/s.
	\item 18650 battery (x2).
	\item 18650 battery charging protection.
	\item 18650 battery holder.
	\item Bluetooth module.
	\item USB female connector.
	\item Hall current sensor.
	\item Voltage sensors (x2).
	\item MOSFETs.
	\item Rotary encoder.
	\item XH-25 pin headers.
	\item Atmega2560 arduino compatible board.
	\item Necessary caps and resistors.
	\item DPDT mini switches.
	\item Relays.
	\item LEDs.
	\item Buzzer.
\end{itemize}




\end{document}